1 Report ASP20 Boost

### 2020-08-18 Reports/term_paper/TERM_PAPER.Rmd
- Changes on final report. - First update of Roxygen comments.

@@

## Concept: Boosting

@@

## Location-Booster

@@

@@

## Scale-Booster

@@

## Functionality: Componentwise Boosting

@@

>>>>

# Abstract

We describe version 1.0 of the R add-on package asp20boost. The package  implements boosting *Note: Expand*. 
Keywords: component-wise boosting,  gradient descent, location and scale.

@@

## Concept: Simple Boosting

@@

### Location-Booster

@@

*Note to self: Add the description of the whole algorithm. Not just the residuals*

@@

### Scale-Booster

@@

## Componentwise Boosting

*Note to self: Add rationale of CWB and motivation for prefering it over simple B*

@@

*Note to self: I pooled all statements of report 1 regarding inplementation on this section. There is thus not coherent argument. Most of it is superfluous. Needs to be updated.*
